On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-08 MS.tex
Lower case pi
Enable png figures to be used over pdf
Removing extension in tex means that latex will take any of a number of graphic extensions
By default, tex preferences png over pdf, so if the png is present that will be used
Instead of changing our figures from pdf in R code, we can instead generate pngs using ImageMagikk's convert function, e.g.  `convert -density 300 -background white -quality 100 "$i" "${i%.*}.png"`

Similarly \textbf{growth rate in basal area} can be expressed as the sum of growth in sapwood and heartwood, with the former term again decomposed as a product:
\begin{equation}\label{eq:eq3}
\begin{array}{ccccc}
\underbrace{{\frac{\ud A_{\rm st}}{\ud t}}}_{\text{basal area growth rate}} &=& \frac{\ud A_{\rm ss}}{\ud t} &+& \frac{\ud A_{\rm sh}}{\ud t} \\
&=& \underbrace{\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}  \times {\frac{\ud A_{\rm l}}{\ud M_{\rm a} }} \times  {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}}_{\text{increase in total sapwood}} &+&  \underbrace{k_{\rm ss} \times \frac{\ud A_{\rm ss}}{\ud t}}_{\text{sapwood turnover}}.\\
\end{array}
\end{equation}
Here $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}} $ is the  sapwood area per leaf area. The \textbf{growth rate in diameter} is then obtained via the geometric relationship between stem diameter and stem area,
\begin{equation}\label{eq:eq4}
\underbrace{\frac{\ud D}{\ud t}}_{\text{growth rate in diameter}} = \left(\Pi \, A_{\rm st}\right)^{-0.5} \times {\frac{\ud A_{\rm st}}{\ud t}}.
\end{equation}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1.pdf}
\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait. Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density. Results shown are from the entire dataset (see methods for details).}
\label{fig:fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2.pdf}
\caption{The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines). Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth. Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses. Studies marked with a ``*'' were those where stage was changed or assigned, compared to the original publication.}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3.pdf}
\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation by ontogenetic stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Results shown are for the "conservative dataset" (i.e. correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage) and for the entire dataset (i.e. with all criteria relaxed, see methods for details). Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage for the conservative dataset. A significant p-value means adding a stage effect to the model significantly improved model fit.}
\label{fig:fig3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4.pdf}
\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along ontogenetic stage. The legend is identical to Fig 3, with two exceptions. i) Results shown are from the entire dataset (see methods for details). ii) Likelihood Ratio Tests compared maximum-likelihood fits between a model separated by stage and one separared by stage and growth measurement (RGR vs AGR).}
\label{fig:fig4}
\end{figure}

>>>>

Similarly \textbf{growth rate in basal area} can be expressed as the sum of growth in sapwood and heartwood, with the former term again decomposed as a product:
\begin{equation}\label{eq:eq3}
\begin{array}{ccccc}
\underbrace{{\frac{\ud A_{\rm st}}{\ud t}}}_{\text{basal area growth rate}} &=& \frac{\ud A_{\rm ss}}{\ud t} &+& \frac{\ud A_{\rm sh}}{\ud t} \\
&=& \underbrace{\frac{\ud A_{\rm ss}}{\ud A_{\rm l}}  \times {\frac{\ud A_{\rm l}}{\ud M_{\rm a} }} \times  {\frac{\ud M_{\rm a} }{\ud B}} \times {\frac{\ud B}{\ud t}}}_{\text{increase in total sapwood}} &+&  \underbrace{k_{\rm ss} \times \frac{\ud A_{\rm ss}}{\ud t}}_{\text{sapwood turnover}}.\\
\end{array}
\end{equation}
Here $\frac{\ud A_{\rm ss}}{\ud A_{\rm l}} $ is the  sapwood area per leaf area. The \textbf{growth rate in diameter} is then obtained via the geometric relationship between stem diameter and stem area,
\begin{equation}\label{eq:eq4}
\underbrace{\frac{\ud D}{\ud t}}_{\text{growth rate in diameter}} = \left(\pi \, A_{\rm st}\right)^{-0.5} \times {\frac{\ud A_{\rm st}}{\ud t}}.
\end{equation}

@@

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig1}
\caption{Number of recorded correlations between trait and growth rate in our dataset, by stage and trait. Traits are: Aarea (or Amass) = rate of CO$_{2}$ assimilation per unit leaf area (or leaf mass) = maximum photosynthetic rate, Hmax = asymptotic or maximum height, Ks = stem hydraulic conductance, LA = leaf area, LMR = leaf mass ratio, NARarea = net mass assimilation rate per unit of leaf area, Nmass (or Narea) = nitrogen content per unit of leaf mass (or leaf area), Pmass = phosphorus content per unit of leaf mass, SA/LA = sapwood area per leaf area, SLA = specific leaf area, Thickness = leaf thickness, Vessel size = stem conduit size, Vessel density = stem conduit density, WD = wood density. Results shown are from the entire dataset (see methods for details).}
\label{fig:fig1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig2}
\caption{The range of plant sizes and stages recorded in original publications (horizontal coloured lines), compared to standardised thresholds used in the analysis (vertical black lines). Horizontal line segments indicate the size range (max., min.) of the plants used to measure growth. Horizontal line colours refer to the original stage attributed by the authors .The solid vertical lines indicate the thresholds used to classify plants in one of three stages in our meta-analyses. Studies marked with a ``*'' were those where stage was changed or assigned, compared to the original publication.}
\label{fig:fig2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig3}
\caption{The relationship between relative growth rates (RGR) and traits changes with ontogenetic stage and trait. Plots show the effect size (+ 95\% confidence intervals; CI) for the average correlation by ontogenetic stage. Effect size is a standardized measure of the deviation of correlation coefficient from zero (Fisher's z-transformed). Effects are significant if CIs for a given stage do not overlap with zero. Trait names as in Fig. \ref{fig:fig1}. $n$ indicates number of correlations contributing to each effect. Results shown are for the "conservative dataset" (i.e. correlations that included \underline{\textgreater} 10 species, under unstressed conditions, and where the trait and growth were measured at the same stage) and for the entire dataset (i.e. with all criteria relaxed, see methods for details). Likelihood Ratio Tests (LRT) compared maximum-likelihood fits between a pooled model and one separated by stage for the conservative dataset. A significant p-value means adding a stage effect to the model significantly improved model fit.}
\label{fig:fig3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/Fig4}
\caption{Relationships between relative (RGR) and/or absolute (AGR) growth rates and traits along ontogenetic stage. The legend is identical to Fig 3, with two exceptions. i) Results shown are from the entire dataset (see methods for details). ii) Likelihood Ratio Tests compared maximum-likelihood fits between a model separated by stage and one separared by stage and growth measurement (RGR vs AGR).}
\label{fig:fig4}
\end{figure}

### 2016-03-08 ms-suppinfo.Rnw
LIzzy comments 1
Enable png figures to be used over pdf
Removing extension in tex means that latex will take any of a number of graphic extensions
By default, tex preferences png over pdf, so if the png is present that will be used
Instead of changing our figures from pdf in R code, we can instead generate pngs using ImageMagikk's convert function, e.g.  `convert -density 300 -background white -quality 100 "$i" "${i%.*}.png"`

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1.pdf}
\caption{Relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height among plants in the Biomass and Allometry Database. Lines indicate the cut-offs between stage categories used in this study: blue lines indicate limit between seedlings and saplings, red lines indicate limits between saplings and adults.}
\label{fig:figA1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b.pdf}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c.pdf}
\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4). a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax). The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form. AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. The smaller the AIC, the better the model is. Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods''). ``n'' indicates number of correlation r reported.}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4.pdf}
\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.  a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea). The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8.pdf}
\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement). a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot. Results shown here are from the ``ideal'' subset of the data (for details see ``Material and Methods''). }
\label{fig:figA8}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2.pdf}
\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the entire dataset (for details see ``Material and Methods'').}
\label{fig:figA2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3.pdf}
\caption{Range of correlations (r) between
growth and traits reported in the literature. Plots show the coefficients of correlation (r)
between plant growth and a) Specific leaf area (SLA, n =
111), b) Wood density (WD, n = 64), c) Asymptotic
maximum height (Hmax, n = 23), d) Seed mass (n = 36) and
e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
articles. The x axis represents the article ID sorted by the average reported coefficient value r. Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e. number of species). The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings. Results shown here are from the entire dataset (for details see ``Material and Methods''). }
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7.pdf}
\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation. The open points correspond to the estimated missing studies. The number of missing values is 4 for SLA, 0 for wood density, 0 for maximum height, 11 for seed mass and 0 for Aarea. Results shown here are from the entire dataset. Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
\label{fig:figA7}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9.pdf}
\caption{Temporal changes in coefficient of correlation between growth and traits. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass, and e) Assimilation rate of CO2 (Aarea). The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings. Results shown here are from the entire dataset.}
\label{fig:figA9}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5.pdf}
\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study. In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if CIs do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data , grey points: all the data (for details see ``Material and Methods''). ``n'' indicates the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA1}
\caption{Relationships between a) age and diameter (m), b) age and height (m), and c) diameter and height among plants in the Biomass and Allometry Database. Lines indicate the cut-offs between stage categories used in this study: blue lines indicate limit between seedlings and saplings, red lines indicate limits between saplings and adults.}
\label{fig:figA1}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6a}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6b}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA6c}
\caption{Effects size on the correlation between growth and traits of plant stage (mod1), growth measurement (mod2), vegetation type (mod3), and experiment type (mod4). a) Specific leaf area (SLA), b) Wood density (WD),c) Assimilation rate of CO2 (Aarea), d) Seed mass, and e) Asymptotic maximum height (Hmax). The effect size (z + 95\%CI) is reported for each class, and models are fitted by restricted max likelihood (REML). Abbreviation: GR = growth rate and RGR = relative growth rate, measured in diameter (D), height (H), mass(M), cross section area (CSA) and volume (V), across GF: coefficient of correlation measured on tree in mixture with other growth form. AIC: Akaike information criterion corresponds to the quality of each model, and allow a comparison between models. The smaller the AIC, the better the model is. Results shown here are from ``ideal'' subset of data (for details see ``Material and Methods''). ``n'' indicates number of correlation r reported.}
\label{fig:figA6}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA4}
\caption{Mean coefficient correlation r (+SD) between growth and traits measured by stage.  a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass (Seedmass) and e) Rate of CO2 assimilation (Aarea). The mean coefficients are weighted by sample size and established from 103 articles. Results shown here are from the ``ideal'' subset of data (for details see ``Material and Methods''), ``n'' indicates the number of correlations.}
\label{fig:figA4}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA8}
\caption{Number of correlation extracted by traits, stage, and growth type (absolute vs relative, and measurement). a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Absolute growth rate (AGR) is on the left and relative growth rate (RGR) on the right of each plot. Results shown here are from the ``ideal'' subset of the data (for details see ``Material and Methods''). }
\label{fig:figA8}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA2}
\caption{Geographical distribution of site locations from studies performed in the field used in the meta-analysis. Results shown here are from the entire dataset (for details see ``Material and Methods'').}
\label{fig:figA2}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA3}
\caption{Range of correlations (r) between
growth and traits reported in the literature. Plots show the coefficients of correlation (r)
between plant growth and a) Specific leaf area (SLA, n =
111), b) Wood density (WD, n = 64), c) Asymptotic
maximum height (Hmax, n = 23), d) Seed mass (n = 36) and
e) Rate of CO2 assimilation (Aarea, n = 24) reported from 103
articles. The x axis represents the article ID sorted by the average reported coefficient value r. Each bubble represents an r value, the diameter of the bubble is proportional to its weight in the meta-analysis (i.e. number of species). The colours correspond to the stage for which the r values have been recorded: red points correspond to adult stage, orange points to saplings, and blue points to seedlings. Results shown here are from the entire dataset (for details see ``Material and Methods''). }
\label{fig:figA3}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA7}
\caption{Funnel plots with filled in data based on the trim and fill method, showing transformed correlation coefficient z between growth and a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass and e) Assimilation rate of CO2 (Aarea). Note that in these plots the y axis is 1/number of species included in the correlation, not the replication for the correlation. The open points correspond to the estimated missing studies. The number of missing values is 4 for SLA, 0 for wood density, 0 for maximum height, 11 for seed mass and 0 for Aarea. Results shown here are from the entire dataset. Results with the "ideal" subset of data (for details see ``Material and Methods''), shown no missing values for all traits.}
\label{fig:figA7}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA9}
\caption{Temporal changes in coefficient of correlation between growth and traits. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax), d) Seed mass, and e) Assimilation rate of CO2 (Aarea). The colours correspond to the stage for which the r values have been recorded: red points corresponds to adult stage, orange points to saplings, and grey points to seedlings. Results shown here are from the entire dataset.}
\label{fig:figA9}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=15cm,height=20cm,keepaspectratio]{output/FigA5}
\caption{Effect size ($\pm$95\% confidence intervals, CI) of plant stage on the correlations between growth rate and five functional traits across species, with a data set averaging multiple comparisons by trait and by study. In the case of multiple comparisons within a study, effect sizes were calculated using the mean correlation coefficient by trait and by study. a) Specific leaf area (SLA), b) Wood density (WD), c) Asymptotic maximum height (Hmax) , d) Seed mass and e) Assimilation rate of CO2 (Aarea). Effect size is a standardized measure of the magnitude of the relationship between a particular stage and the correlation coefficient z (Fisher's z-transformed). Effects are significant if CIs do not overlap with zero. LRT: likelihood Ratio Test compared the fit between null model and stage model, both models are fitted by Maximum Likelihood. Black point: ideal data , grey points: all the data (for details see ``Material and Methods''). ``n'' indicates the number of independent comparisons for each effect.}
\label{fig:figA5}
\end{figure}
